\section*{Acknowledgments}

\addcontentsline{toc}{section}{Acknowledgments}

I would like to express my deepest gratitude to Dr Charitha de Silva for your exceptional guidance, support, and mentorship throughout this thesis. Your willingness to offer help beyond expectation, whether through detailed feedback, thoughtful direction, or encouragement during challenging stages, has been invaluable to both my academic development and the success of this project. I am sincerely thankful for the trust you placed in me and for the opportunity to grow under your supervision.

I extend my sincere appreciation to Matthew Deng, whose dedication to this project has been truly inspiring. Thank you for running experimental tests on weekends, for troubleshooting ideas through long discussions, and for consistently sharing your knowledge with patience and enthusiasm. Your support has been invaluable, and it has been a privilege to learn from you and work alongside you. As you continue this project beyond the completion of my thesis, I wish you every success in both your PhD and your future career.

I would also like to thank Shubhneet Sodhi, without whom this journey would not have been the same. From late-night calls to early-morning problem-solving sessions, your support, friendship, and shared determination transformed an intimidating task into one of the most rewarding experiences of my time at university. I feel incredibly fortunate that we completed this thesis together. In the first trimester, I wrote that by the end we might finally feel as though we had earned the break. Now that the break is approaching, it is clear that the exhaustion we once felt has become a testament to that effort. This experience has reminded me that challenge is inseparable from purpose, and I remain grateful for such exceptional company.

Finally, I am grateful to my family and friends for their unwavering patience and support. Your willingness to listen, even when I spoke at length about concepts far removed from your own interests, has meant more to me than I can express. Your kindness, encouragement, and constant presence have made me feel incredibly fortunate. Any success I achieve, I owe to all of you.
