\begin{comment}
The following are intended to provide examples of the different reference types. You are not required to indicate the type of reference; different types are shown here for illustrative purposes only. You are welcome to use slightly different referencing formats – whenever you are in google scholar and click on “cite”, you get the three most popular and standard referencing layouts. We don’t mind if you prefer to go alphabetical rather than numbers in this list and correspondingly in the text, or whatever your supervisor prefers. \textit{Just be consistent all the way through!} \\

Periodicals \\
$^1$Vatistas, G. H., Lin, S., and Kwok, C. K., “Reverse Flow Radius in Vortex Chambers,” \textit{AIAA Journal}, Vol. 24, No. 11, 1986, pp. 1872, 1873. \\
$^2$Dornheim, M. A., “Planetary Flight Surge Faces Budget Realities,” \textit{Aviation Week and Space Technology}, Vol. 145, No. 24, 9 Dec. 1996, pp. 44-46. \\
$^3$Terster, W., “NASA Considers Switch to Delta 2,” \textit{Space News}, Vol. 8, No. 2, 13-19 Jan. 1997, pp., 1, 18. \\

All of the preceding information is required. The journal issue number (“No. 11” in Ref. 1) is preferred, but the month (Nov.) can be substituted if the issue number is not available. Use the complete date for daily and weekly publications. Transactions follow the same style as other journals; if punctuation is necessary, use a colon to separate the transactions title from the journal title. \\

Books \\
$^4$Peyret, R., and Taylor, T. D., \textit{Computational Methods in Fluid Flow}, 2nd ed., Springer-Verlag, New York, 1983, Chaps. 7, 14. \\
$^5$Oates, G. C. (ed.), \textit{Aerothermodynamics of Gas Turbine and Rocket Propulsion}, AIAA Education Series, AIAA, New York, 1984, pp. 19, 136. \\
$^6$ Volpe, R., “Techniques for Collision Prevention, Impact Stability, and Force Control by Space Manipulators,” \textit{Teleoperation and Robotics in Space}, edited by S. B. Skaar and C. F. Ruoff, Progress in Astronautics and Aeronautics, AIAA, Washington, DC, 1994, pp. 175-212. \\

Publisher, place, and date of publication are required for all books. No state or country is required for major cities: New York, London, Moscow, etc. A differentiation must always be made between Cambridge, MA, and Cambridge, England, UK. Note that series titles are in roman type. \\

Proceedings \\
$^7$Thompson, C. M., “Spacecraft Thermal Control, Design, and Operation,” \textit{AIAA Guidance, Navigation, and Control Conference}, CP849, Vol. 1, AIAA, Washington, DC, 1989, pp. 103-115 \\
$^8$Chi, Y., (ed.), \textit{Fluid Mechanics Proceedings}, SP-255, NASA, 1993. \\
$^9$Morris, J. D. “Convective Heat Transfer in Radially Rotating Ducts,” \textit{Proceedings of the Annual Heat Transfer Conference}, edited by B. Corbell, Vol. 1, Inst. Of Mechanical Engineering, New York, 1992, pp. 227-234. \\

At a minimum, proceedings must have the same information as other book references: paper (chapter) and volume title, name and location of publisher, editor (if applicable), and pages or chapters cited. Do not include paper numbers in proceedings references, and delete the conference location so that it is not confused with the publisher’s location (which is mandatory, except for government agencies). Frequently, CP or SP numbers (Conference Proceedings or Symposium Proceedings numbers) are also given. These elements are not necessary, but when provided, their places should be as shown in the preceding examples. \\

Reports, Theses, and Individual Papers \\
$^{10}$Chapman, G. T., and Tobak, M., “Nonlinear Problems in Flight Dynamics,” NASA TM-85940, 1984. \\
$^{11}$Steger, J. L., Jr., Nietubicz, C. J., and Heavey, J. E., “A General Curvilinear Grid Generation Program for Projectile Configurations,” U.S. Army Ballistic Research Lab., Rept. ARBRL-MR03142, Aberdeen Proving Ground, MD, Oct. 1981. \\
$^{12}$Tseng, K., “Nonlinear Green’s Function Method for Transonic Potential Flow,” Ph.D. Dissertation, Aeronautics and Astronautics Dept., Boston Univ., Cambridge, MA, 1983. \\

Government agency reports do not require locations. For reports such as NASA TM-85940, neither insert nor delete dashes; leave them as provided by the author. Place of publication should be given, although it is not mandatory, for military and company reports. Always include a city and state for universities. Papers need only the name of the sponsor; neither the sponsor’s location nor the conference name and location are required. Do not confuse proceedings references with conference papers. \\

Electronic Publications \\
CD-ROM publications and regularly issued, dated electronic journals are permitted as references. Archived data sets also may be referenced as long as the material is openly accessible and the repository is committed to archiving the data indefinitely. References to electronic data available only from personal Web sites or commercial, academic, or government ones where there is no commitment to archiving the data are not permitted (see Private Communications and Web sites). \\

$^{13}$Richard, J. C., and Fralick, G. C., “Use of Drag Probe in Supersonic Flow,” \textit{AIAA Meeting Papers on Disc} [CD-ROM], Vol. 1, No. 2, AIAA, Reston, VA, 1996. \\
$^{14}$Atkins, C. P., and Scantelbury, J. D., “The Activity Coefficient of Sodium Chloride in a Simulated Pore Solution Environment,” \textit{Journal of Corrosion Science and Engineering} [online journal], Vol. 1, No. 1, Paper 2, URL: \underline{http://www.cp/umist.ac.uk/JCSE/vol1/vol1.html} [cited 13 April 1998]. \\
$^{15}$Vickers, A., “10-110 mm/hr Hypodermic Gravity Design A,” \textit{Rainfall Simulation Database} [online database], URL: \underline{http://www.geog.le.ac.uk/bgrg/lab.htm} [cited 15 March 1998]. \\

Always include the citation date for online references. Break Web site addresses after punctuation, and do not hyphenate at line breaks. \\

Computer Software \\
$^{16}$TAPP, Thermochemical and Physical Properties, Software Package, Ver. 1.0, E. S. Microware, Hamilton, OH, 1992. \\

Include a version number and the company name and location of software packages. \\

Patents \\
Patents appear infrequently. Be sure to include the patent number and date.
$^{17}$Scherrer, R., Overholster, D., and Watson, K., Lockheed Corp., Burbank, CA, U.S. Patent Application for a “Vehicle,” Docket No. P-01-1532, filed 11 Feb. 1979. \\

Private Communications and Web Sites
References to private communications and personal Web site addresses are generally not permitted. Private communications can be defined as privately held unpublished letters or notes or conversations between an author and one or more individuals. They may be cited as references in some case studies, but only with permission of the AIAA staff. Depending on the circumstances, private communications and Web site addresses may be incorporated into the main text of a manuscript or may appear in footnotes. \\

Unpublished Papers and Books
Unpublished works can be used as references as long as they are being considered for publication or can be located by the reader (such as papers that are part of an archival collection). If a journal paper or a book is being considered for publication choose the format that reflects the status of the work (depending upon whether it has been accepted for publication): \\

$^{18}$Doe, J., “Title of Paper,” Conference Name, Publisher’s name and location (submitted for publication) \\
$^{19}$Doe, J., “Title of Paper,” \textit{Name of Journal} (to be published). \\
$^{20}$Doe, J., “Title of Chapter,” \textit{Name of Book}, edited by… Publisher’s name and location (to be published). \\
$^{21}$Doe, J., “Title of Work,” Name of Archive, Univ. (or organization) Name, City, State, Year (unpublished). \\

Unpublished works in an archive must include the name of the archive and the name and location of the university or other organization where the archive is held. Also include any cataloging information that may be provided. Always query for an update if a work is about to be published.

\pagebreak
\end{comment}